Edge sign prediction in general graphs and connection with Correlation Clustering

### 2017-06-30 assets/tikz/gtx_cross_edges_tikz.tex
typo: change name of stars in cross_edges figure

  \draw[draw=none, fill opacity=.7, fill=Red] (-.30,-1.5) -- (.77,-3.34) -- (2.34,-2.42) -- (1.37,-.77) -- cycle;
  \draw[star] (0,0) circle [radius=1.7]  node[star-label,xshift=-30, yshift=25] {${S_1^1}$};
  \draw[star] (2.189,-3.948) circle [radius=1.7]  node[star-label,xshift=30, yshift=0] {${S_2^1}$};

>>>>

  \draw[draw=none, fill opacity=.7, fill=Red] (-.30,-1.5) -- (.77,-3.34) -- (2.34,-2.42) -- (1.37,-.77) -- cycle;
  \draw[star] (0,0) circle [radius=1.7]  node[star-label,xshift=-30, yshift=25] {${s_1}$};
  \draw[star] (2.189,-3.948) circle [radius=1.7]  node[star-label,xshift=30, yshift=0] {${s_2}$};
